---
subtitle: "Week 2 Report"
date: 2026-09-29
params:
  season: 2026
  week: 2
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
source(here::here("R/fleaflicker.R"))
source(here::here("R/analytics.R"))
source(here::here("R/tables.R"))
source(here::here("R/theme.R"))

#knitr::opts_chunk$set(dev = "ragg_png")

LEAGUE_ID <- 23701
SPORT     <- "NFL"
SEASON    <- params$season
WEEK      <- params$week
DATE      <- Sys.Date()
```

# Weekly Report

**Season:** `r SEASON`\
**Week:** `r WEEK`\
**Report Date:** `r DATE`

```{r load-data, include=FALSE}
data <- get_week_cached(LEAGUE_ID, SPORT, SEASON, WEEK)
player_stats             <- data$player_stats
scoreboard               <- data$scoreboard
team_optimal_scores_data <- data$team_optimal_scores

standings_data <- get_league_standings(LEAGUE_ID, SPORT, SEASON)

matchups       <- get_matchup_results(scoreboard)
team_scores    <- calculate_team_scores(player_stats)
pos_stats      <- analyze_position_performance(player_stats)
best_bench     <- find_best_bench_players(player_stats)
worst_starters <- find_worst_starters(player_stats)
optimal_scores <- calculate_optimal_scores(team_optimal_scores_data)

highest_scorer <- team_scores$fantasy_team_name[1]
highest_score  <- team_scores$total_points[1]
lowest_scorer  <- team_scores$fantasy_team_name[nrow(team_scores)]
lowest_score   <- team_scores$total_points[nrow(team_scores)]
avg_score      <- mean(team_scores$total_points)
```

```{r load-multi-week-data, include=FALSE}
divisions      <- get_divisions(standings_data)
all_weeks_data <- get_season_to_date(LEAGUE_ID, SPORT, SEASON, WEEK) |>
  normalize_team_names(divisions)

all_player_data <- bind_rows(lapply(all_weeks_data, `[[`, "player_stats")) |>
  left_join(select(divisions, fantasy_team_id, division), by = "fantasy_team_id")

weekly_scores <- weekly_team_scores(all_weeks_data)
```

::: {.callout-note icon="false"}
## Week `r WEEK` Overview

- **Highest Scorer:** `r team_scores$fantasy_team_name[1]` (`r sprintf("%.2f", team_scores$total_points[1])` pts)
- **Lowest Scorer:** `r team_scores$fantasy_team_name[nrow(team_scores)]` (`r sprintf("%.2f", team_scores$total_points[nrow(team_scores)])` pts)
- **Score Differential:** `r sprintf("%.2f", highest_score - lowest_score)` pts
- **Average Score:** `r sprintf("%.2f", mean(team_scores$total_points))` pts
:::

## 📋 Matchup Results

```{r matchups}
# Add winner and margin columns
matchups$Winner <- ifelse(matchups$away_score > matchups$home_score, 
                          matchups$away_team, matchups$home_team)
matchups$Margin <- abs(matchups$away_score - matchups$home_score)
matchups$Status <- ifelse(matchups$Margin < 5, "🔥 Close Game",
                          ifelse(matchups$Margin > 30, "💥 Blowout", ""))

# Display table
kable(matchups[, c("away_team", "away_score", "home_team", "home_score", "Winner", "Margin", "Status")],
      col.names = c("Away Team", "Away Score", "Home Team", "Home Score", "Winner", "Margin", "Status"),
      digits = 2,
     align = c("l", "l", "r", "c", "c", "c", "r"), 
      ) |>
  column_spec(1, width = "11em") |>
  column_spec(3, width = "11em") |>
  column_spec(5, width = "11em") |>
  column_spec(7, width = "8em") 
```

## 🏆 Team Rankings - This Week

```{r team-standings}
# Add rank column
team_scores$Rank <- 1:nrow(team_scores)

# Add medals
team_scores$Medal <- ""
team_scores$Medal[1] <- "🥇"
if (nrow(team_scores) >= 2) team_scores$Medal[2] <- "🥈"
if (nrow(team_scores) >= 3) team_scores$Medal[3] <- "🥉"

# Display table
kable(team_scores[, c("Medal", "Rank", "fantasy_team_name", "total_points")],
      col.names = c("", "Rank", "Team Name", "Total Points"),
      digits = 2,
      align = c("c", "c", "l", "r"),
      row.names = FALSE)
```

## 🏳️‍🌈 Glekas Card Tracker

```{r glekas-card}
# Parse league standings to get all teams with playoff seeding
all_teams <- list()

if (!is.null(standings_data) && "divisions" %in% names(standings_data)) {
  for (division in standings_data$divisions) {
    if ("teams" %in% names(division)) {
      for (team in division$teams) {
        team_info <- data.frame(
          team_id = if (!is.null(team$id)) team$id else NA,
          team_name = if (!is.null(team$name)) team$name else NA,
          overall_rank = if (!is.null(team$recordOverall$rank)) team$recordOverall$rank else NA,
          playoff_seed = if (!is.null(team$recordPostseason$rank)) team$recordPostseason$rank else NA,
          points_for = if (!is.null(team$pointsFor$value)) team$pointsFor$value else NA,
          overall_record = if (!is.null(team$recordOverall$formatted)) team$recordOverall$formatted else NA,
          stringsAsFactors = FALSE
        )
        all_teams[[length(all_teams) + 1]] <- team_info
      }
    }
  }
}

teams_standings <- do.call(rbind, all_teams) %>%
  arrange(playoff_seed)

# Get 6th playoff seed
sixth_seed <- teams_standings %>% filter(playoff_seed == 6)

# Get 7-12 playoff seeds
wildcard_contenders <- teams_standings %>% filter(playoff_seed >= 7 & playoff_seed <= 12)

# Check if any 7-12 seed has more Points For than 6th seed
glekas_eligible <- wildcard_contenders %>%
  filter(points_for > sixth_seed$points_for) %>%
  arrange(desc(points_for))

# Create display table
glekas_table <- teams_standings %>%
  filter(playoff_seed >= 6 & playoff_seed <= 12) %>%
  mutate(
    status = case_when(
      playoff_seed == 6 ~ "Current #6 Seed",
      team_id %in% glekas_eligible$team_id ~ "🃏 Glekas Card Active!",
      TRUE ~ "Out of Contention"
    ),
    points_diff = points_for - sixth_seed$points_for
  ) %>%
  arrange(playoff_seed)

glekas_table %>%
  select(playoff_seed, team_name, overall_record, points_for, points_diff, status) %>%
  kable(
    col.names = c("Playoff Seed", "Team", "Record", "Points For", "Diff from #6", "Status"),
    digits = 2,
    align = c('c', 'l', 'c', 'c', 'c', 'r')
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  row_spec(which(glekas_table$playoff_seed == 6), background = "#fff3cd") %>%
  row_spec(which(glekas_table$team_id %in% glekas_eligible$team_id), 
           background = "#d4edda", bold = TRUE)
```

::: {.callout-tip icon="false"}
## 🃏 Glekas Card Rule

The #6 playoff seed can be replaced by any team seeded #7-#12 if they have higher total Points For on the season.

**Current Situation:**

`r if(nrow(glekas_eligible) > 0) {   paste0("✅ **", glekas_eligible$team_name[1], "** (Playoff Seed #", glekas_eligible$playoff_seed[1], ") would replace **", sixth_seed$team_name, "** with ", sprintf("%.2f", glekas_eligible$points_for[1]), " Points For vs ", sprintf("%.2f", sixth_seed$points_for), " Points For!") } else {   paste0("❌ No Glekas Card applies - **", sixth_seed$team_name, "** holds the #6 playoff seed with ", sprintf("%.2f", sixth_seed$points_for), " Points For") }`
:::

```{r glekas-chart}
#| fig-width: 10.25
#| fig-height: 6

# Visualize Glekas Card situation
glekas_chart_data <- teams_standings %>%
  filter(playoff_seed >= 6 & playoff_seed <= 12) %>%
  mutate(
    is_sixth = playoff_seed == 6,
    is_glekas = team_id %in% glekas_eligible$team_id,
    fill_color = case_when(
      is_sixth ~ "Current #6",
      is_glekas ~ "Glekas Active",
      TRUE ~ "Other"
    )
  )

ggplot(glekas_chart_data,
       aes(x = reorder(team_name, -playoff_seed), y = points_for, fill = fill_color)) +
  geom_col() +
  geom_hline(yintercept = sixth_seed$points_for,
             linetype = "dashed", color = brand[["red"]], linewidth = 1) +
  annotate("text", x = 0.5, y = sixth_seed$points_for,
           label = sprintf("6th Seed Threshold: %.1f", sixth_seed$points_for),
           vjust = -0.5, color = brand[["red"]], size = 3.5) +
  geom_text(aes(label = sprintf("%.0f", points_for)), hjust = -0.5, size = 3) +
  coord_flip() +
  scale_fill_manual(values = c("Current #6"   = brand[["orange"]],
                               "Glekas Active" = brand[["green"]],
                               "Other"         = brand[["slate"]])) +
  labs(title = "Glekas Card Tracker - Points For Comparison",
       subtitle = "Teams above the dashed line would claim the #6 playoff spot",
       x = "Team (by Playoff Seed)",
       y = "Season Points For",
       fill = NULL)
```

## 📊 Score Distribution

```{r score-distribution}
#| fig-width: 10
#| fig-height: 6

p <- ggplot(team_scores, aes(x = total_points)) +
  geom_histogram(bins = 8, fill = "#3498db", alpha = 0.7, color = "black") +
  geom_vline(aes(xintercept = mean(total_points)), 
             color = "red", linetype = "dashed", size = 1) +
  annotate("text", x = mean(team_scores$total_points), 
           y = Inf, label = sprintf("Avg: %.1f", mean(team_scores$total_points)),
           vjust = 2, hjust = -.25, color = "red", size = 5) +
  labs(title = "Score Distribution Across Teams",
       x = "Points Scored",
       y = "Number of Teams") +
  theme_minimal(base_size = 16) +
  theme(plot.title = element_text(hjust = 0.5, size = 16, face = "bold"))

# Display in document
print(p)

# Save as thumbnail
ggsave("thumbnail.jpg", p, width = 6.67, height = 4.45, dpi = 96)

```

## ⭐ Top Performers

### Top 10 Starters

```{r top-performers}
top_players <- player_stats[order(-player_stats$points), ]
top_starters <- top_players[top_players$lineup_group == "START", ][1:10, ]
top_starters$Rank <- 1:nrow(top_starters)

# Add colored position tiles
top_starters$Position_Colored <- sapply(top_starters$position, color_position)

kable(top_starters[, c("Rank", "player_name", "Position_Colored", "nfl_team", "opponent", "points", "fantasy_team_name")],
      format = "html",
      col.names = c("Rank", "Player", "Pos", "Team", "Opp", "Points", "Fantasy Team"),
      digits = 2,
      align = c("c", "l", "c", "c", "c", "r", "r"),
      row.names = FALSE,
      escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)
```

## 🏈 Position Analysis

```{r position-analysis}
pos_stats$Position_Colored <- sapply(pos_stats$position, color_position)

kable(pos_stats[, c("Position_Colored", "count", "avg", "max", "min", "total")],
      format = "html",
      col.names = c("Position", "# Players", "Avg Points", "Highest Points", "Lowest Points", "Total Points"),
      digits = 2,
      align = c("c", "c", "c", "c", "c", "c"),
      row.names = FALSE,
      escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)
```

## 😞 Worst Lineup Decisions

### Bottom 10 Starters

```{r worst-starters}
worst_starters$Rank <- 1:nrow(worst_starters)

# Add colored position tiles
worst_starters$Position_Colored <- sapply(worst_starters$position, color_position)

kable(worst_starters[, c("Rank", "player_name", "Position_Colored", "nfl_team", "opponent", "points", "fantasy_team_name")],
      format = "html",
      col.names = c("Rank", "Player", "Pos", "Team", "Opp", "Points", "Fantasy Team"),
      digits = 2,
      align = c("c", "l", "c", "c", "c", "c", "r"),
      row.names = FALSE,
      escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), 
                full_width = FALSE)
```

## 🤦 Missed Opportunities

::: {.callout-tip icon="false"}
## Points Left on the Bench

These benched players scored MORE than a starter in their position - wasted points!
:::

```{r bench-analysis}
# Create position slot mapping for flex eligibility
position_slots <- list(
  QB = c("QB"),
  RB = c("RB", "RB/WR/TE"),
  WR = c("WR", "RB/WR/TE"),
  TE = c("TE", "RB/WR/TE"),
  K = c("K"),
  "D/ST" = c("D/ST")
)

# Calculate true missed opportunities
missed_opportunities <- list()

teams <- unique(player_stats$fantasy_team_name)

for (team in teams) {
  team_data <- player_stats %>% filter(fantasy_team_name == team)
  
  # Get bench players
  bench <- team_data %>% filter(lineup_group == "BENCH")
  
  if (nrow(bench) == 0) next
  
  for (i in 1:nrow(bench)) {
    bench_player <- bench[i, ]
    
    # Skip if bench player has NA points
    if (is.na(bench_player$points)) next
    
    # Get eligible slots for this position
    eligible_slots <- position_slots[[bench_player$position]]
    
    if (is.null(eligible_slots)) next
    
    # Find starters in eligible slots
    eligible_starters <- team_data %>%
      filter(
        lineup_group == "START",
        slot %in% eligible_slots,
        !is.na(points)  # Exclude starters with NA points
      )
    
    if (nrow(eligible_starters) == 0) next
    
    # Find the WORST starter in eligible slots (who should have been benched)
    worst_starter <- eligible_starters %>%
      arrange(points) %>%
      head(1)
    
    # Calculate opportunity cost
    opportunity_cost <- bench_player$points - worst_starter$points
    
    # Only include if bench player scored more than at least one starter
    # Check for NA and ensure positive opportunity cost
    if (!is.na(opportunity_cost) && !is.na(bench_player$points) && 
        !is.na(worst_starter$points) && opportunity_cost > 0) {
      missed_opp <- data.frame(
        team = team,
        bench_player = bench_player$player_name,
        bench_position = bench_player$position,
        bench_nfl_team = bench_player$nfl_team,
        bench_opponent = bench_player$opponent,
        bench_points = bench_player$points,
        should_have_replaced = worst_starter$player_name,
        starter_position = worst_starter$position,
        starter_points = worst_starter$points,
        opportunity_cost = opportunity_cost,
        stringsAsFactors = FALSE
      )
      
      missed_opportunities[[length(missed_opportunities) + 1]] <- missed_opp
    }
  }
}

if (length(missed_opportunities) > 0) {
  missed_opp_df <- do.call(rbind, missed_opportunities) %>%
    arrange(desc(opportunity_cost)) %>%
    head(10)
  
  missed_opp_df %>%
    mutate(rank = row_number()) %>%
    select(rank, bench_player, bench_position, bench_nfl_team, bench_points, 
           should_have_replaced, starter_points, opportunity_cost, team) %>%
    kable(
      col.names = c("Rank", "Bench Player", "Pos", "Team", "Bench Pts", 
                    "Should Replace", "Starter Pts", "Lost Pts", "Fantasy Team"),
      digits = 2,
      align = c('c', 'l', 'c', 'c', 'c', 'l', 'c', 'c', 'l')
    ) %>%
    kable_styling(
      bootstrap_options = c("striped", "hover"),
      full_width = FALSE
    ) %>%
    row_spec(1:3, background = "#fff3cd")
} else {
  cat("No missed opportunities this week - all teams made optimal lineup decisions!\n")
}
```

```{r bench-chart}
#| fig-width: 10
#| fig-height: 6
if (length(missed_opportunities) > 0 && nrow(missed_opp_df) > 0) {
  # Define custom team colors
  team_colors <- c(
  "Estyfied" = "#e74c3c",        # Red
  "One for the Thumb in 21" = "#3498db",  # Blue
  "It's Geno Time!" = "#2ecc71",          # Green
  "Activate Winning" = "#8b4513",               # Brown
  "Thumb the Punt" = "#ff6b6b",                  # Coral
  "Ass Bongos" = "#9b59b6",               # Purple
  "Ginger Genius" = "#f39c12",            # Orange
  "You flew here to do this?" = "#1abc9c", # Turquoise
  "Shaboozy 4 The Win!🥇" = "#3D3D3D",     # Dark Gray
  "I love kicking part" = "#ffe0c9",               # Dark Orange
  "Daddysagirl" = "#95a5a6",                  # Gray
  "DaBlacGodfather" = "#0F1056"           # Navy
)
  
  missed_opp_df %>%
  head(10) %>%
  mutate(player_label = paste0(bench_player, " (", bench_position, ")"),
         comparison   = paste0("vs ", should_have_replaced)) %>%
  ggplot(aes(x = reorder(player_label, opportunity_cost), y = opportunity_cost, fill = team)) +
  geom_col() +
  geom_text(aes(label = sprintf("+%.1f pts", opportunity_cost)), hjust = -0.2, size = 4) +
  coord_flip() +
  scale_fill_team() +
  labs(title = "Top Missed Opportunities - Points Left on Bench",
       subtitle = "Points gained if bench player had started instead",
       x = "Bench Player (Position)",
       y = "Missed Points") +
  ylim(0, max(missed_opp_df$opportunity_cost) * 1.15)
}
```

## 🎯 Lineup Efficiency

```{r lineup-efficiency}
if (!is.null(optimal_scores) && nrow(optimal_scores) > 0) {
  # Add efficiency icon
  optimal_scores$Icon <- ifelse(optimal_scores$efficiency >= 95, "🎯",
                                 ifelse(optimal_scores$efficiency >= 85, "✓", "⚠"))
  
  kable(optimal_scores[, c("Icon", "team", "actual_score", "optimal_score", "efficiency", "points_left")],
        col.names = c("", "Team", "Actual", "Optimal", "Efficiency %", "Points Left"),
        digits = c(0, 0, 2, 2, 1, 2),
        align = c("c", "l", "c", "c", "c", "c"),
        row.names = FALSE)
} else {
  cat("Lineup efficiency data not available for this week.\n")
}
```

# Season Trends

::: {.callout-note icon="false"}
## 📊 Multi-Week Analysis

Analysis based on weeks 1-`r WEEK` of the season
:::

## ⛳ Division Performance

```{r division-stats}


# Calculate division statistics
division_stats <- weekly_scores %>%
  left_join(
    all_player_data %>% distinct(fantasy_team_name, division),
    by = "fantasy_team_name"
  ) %>%
  filter(!is.na(division)) %>%
  group_by(division) %>%
  summarise(
    teams = n_distinct(fantasy_team_name),
    avg_points_per_week = mean(total_points, na.rm = TRUE),
    total_points_season = sum(total_points, na.rm = TRUE),
    highest_weekly_score = max(total_points, na.rm = TRUE),
    lowest_weekly_score = min(total_points, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(avg_points_per_week))

division_stats %>%
  kable(
    col.names = c("Division", "Teams", "Avg Pts/Week", "Total Season Pts", "Highest Weekly", "Lowest Weekly"),
     align = c('l', 'c', 'c', 'c', 'c', 'c'),
    digits = 2
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  row_spec(1, background = "#d4edda")
```

```{r division-trends-chart}
#| fig-width: 10
#| fig-height: 6

# Division trends over time
division_weekly <- weekly_scores %>%
  left_join(
    all_player_data %>% distinct(fantasy_team_name, division),
    by = "fantasy_team_name"
  ) %>%
  filter(!is.na(division)) %>%
  group_by(week, division) %>%
  summarise(avg_points = mean(total_points, na.rm = TRUE), .groups = "drop")

ggplot(division_weekly, aes(x = week, y = avg_points, color = division, group = division)) +
  geom_line(linewidth = 1.5) +
  geom_point(size = 3) +
  scale_x_continuous(breaks = 1:WEEK) +
  scale_color_manual(values = unname(brand[c("navy", "orange", "green", "red")])) +
  labs(title = "Division Performance Over Time",
       subtitle = "Average points per team by division",
       x = "Week",
       y = "Average Points")
```

## ⚽ Position Scoring Trends

```{r position-trends}
# Analyze position scoring trends over time
position_trends <- all_player_data %>%
  filter(lineup_group == "START", !is.na(position), !is.na(points)) %>%
  group_by(week, position) %>%
  summarise(
    avg_points = mean(points, na.rm = TRUE),
    count = n(),
    .groups = "drop"
  )

# Summary table
position_summary <- position_trends %>%
  group_by(position) %>%
  summarise(
    weeks = n_distinct(week),
    overall_avg = mean(avg_points, na.rm = TRUE),
    highest_week = max(avg_points, na.rm = TRUE),
    lowest_week = min(avg_points, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(overall_avg))


position_summary %>%
  mutate(position = as.character(position),
         position = color_position(position)) %>%
  kable(
    format = "html",
    col.names = c("Position", "Weeks", "Season Avg", "Best Week", "Worst Week"),
    align = c("l", "c", "c", "c", "c"),
    digits = 2,
    escape = FALSE              
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  )

```

```{r position-trends-chart}
#| fig-width: 10
#| fig-height: 6

# Define colors
position_colors <- c(
  "QB"   = "#FF6B6B",   # Red
  "RB"   = "#9B59B6",   # Purple
  "WR"   = "#2ECC71",   # Emerald green
  "TE"   = "#FFA07A",   # Orange
  "K"    = "#95A5A6",   # Gray
  "D/ST" = "#45B7D1",   # Blue
  "DEF"  = "#45B7D1"    # Blue
)

# Plot
ggplot(position_trends, aes(x = week, y = avg_points, color = position, group = position)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2) +
  scale_color_manual(values = position_colors) +
  scale_x_continuous(breaks = 1:WEEK) +
  labs(title = "Position Scoring Trends",
       subtitle = "Average points by position over the season",
       x = "Week",
       y = "Average Points")
```

## 🎲 Team Consistency

```{r consistency-metrics}
# Calculate consistency (coefficient of variation)
consistency <- weekly_scores %>%
  group_by(fantasy_team_name) %>%
  summarise(
    avg_score = mean(total_points, na.rm = TRUE),
    std_dev = sd(total_points, na.rm = TRUE),
    coefficient_variation = (std_dev / avg_score) * 100,
    weeks_played = n(),
    highest_score = max(total_points, na.rm = TRUE),
    lowest_score = min(total_points, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(coefficient_variation) %>%
  mutate(consistency_rank = row_number())

consistency %>%
  select(consistency_rank, fantasy_team_name, avg_score, std_dev, 
         coefficient_variation, highest_score, lowest_score) %>%
  kable(
    col.names = c("Rank", "Team", "Avg Score", "Std Dev", "CV %", "High", "Low"),
    align = c("c", "l", "c", "c", "c", "c", "c"),
    digits = 2
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  row_spec(1:3, background = "#d4edda")
```

::: {.callout-tip icon="false"}
## 📈 Understanding Consistency

**Coefficient of Variation (CV)** measures scoring volatility:

- **Lower CV** = More consistent (steady scoring each week)
- **Higher CV** = Boom/bust team (high variance in scores)

A CV under 15% is very consistent, while over 25% indicates high volatility.
:::

```{r consistency-chart}
#| fig-width: 10
#| fig-height: 6

ggplot(consistency, aes(x = reorder(fantasy_team_name, -coefficient_variation),
                        y = coefficient_variation, fill = fantasy_team_name)) +
  geom_col(show.legend = FALSE) +
  geom_hline(yintercept = 15, linetype = "dashed", color = brand[["green"]], linewidth = 1) +
  geom_hline(yintercept = 25, linetype = "dashed", color = brand[["red"]], linewidth = 1) +
  coord_flip() +
  scale_fill_team() +
  labs(title = "Team Consistency Rankings",
       subtitle = "Lower CV = more consistent. Green line = very consistent, red line = high volatility",
       x = NULL,
       y = "Coefficient of Variation (%)")
```

## 💩 Shit Tier Rankings

```{r who-sucks-analysis}
# Build the "Who Sucks?" Index
teams_standings_suck <- teams_standings %>%
  mutate(
    # Calculate games played and win percentage
    games_played = ifelse(!is.na(overall_record), 
                         str_extract(overall_record, "\\d+(?=-)") %>% as.numeric() +
                         str_extract(overall_record, "(?<=-)\\d+") %>% as.numeric(), 
                         0),
    wins = ifelse(!is.na(overall_record), 
                 str_extract(overall_record, "\\d+(?=-)") %>% as.numeric(), 
                 0),
    losses = ifelse(!is.na(overall_record), 
                   str_extract(overall_record, "(?<=-)\\d+") %>% as.numeric(), 
                   0),
    win_pct = ifelse(games_played > 0, wins / games_played, 0),
    
    # Scale metrics so higher = more suck
    # We NEGATE the good stuff (wins, points for) 
    suck_win_pct = -scale(win_pct)[, 1],           # lower win% = higher suck
    suck_pf = -scale(points_for)[, 1],             # lower points for = higher suck
    suck_index = suck_win_pct + suck_pf            # Combined suck score
  ) %>%
  arrange(desc(suck_index)) %>%
  mutate(suck_rank = row_number())

# Get the worst and best teams
worst_team <- teams_standings_suck %>% slice(1)
best_team <- teams_standings_suck %>% slice(n())
```

::: {.callout-warning icon="false"}
## 🤡 The "Suck Index"

A scientific™ measure of fantasy football futility combining:

- **Win %** - Losing is sucking
- **Points For** - Low scoring is sucking
- **Higher index** = more suck
:::

```{r who-sucks-table}
teams_standings_suck %>%
  select(suck_rank, team_name, overall_record, win_pct, points_for, suck_index) %>%
  kable(
    col.names = c("Shit Rank", "Team", "Record", "Win %", "Points For", "Suck Index"),
    digits = 2,
    align = c('c', 'l', 'c', 'c', 'r', 'r')
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  row_spec(1, background = "#f8d7da", bold = TRUE) %>%  # Worst team in red
  row_spec(nrow(teams_standings_suck), background = "#d4edda") %>%  # Best team in green
  row_spec(2:3, background = "#fff3cd")  # Runner-ups in yellow
```

::: {.callout-important icon="false"}
## 🏆 Shit Champion

**`r worst_team$team_name`** officially sucks the most with a Suck Index of **`r sprintf("%.2f", worst_team$suck_index)`**!

- Record: `r worst_team$overall_record` (`r sprintf("%.1f%%", worst_team$win_pct * 100)` win rate)
- Points For: `r sprintf("%.2f", worst_team$points_for)`
- Current Playoff Seed: \#`r worst_team$playoff_seed`

Meanwhile, **`r best_team$team_name`** sucks the least with a Suck Index of **`r sprintf("%.2f", best_team$suck_index)`**.
:::

```{r who-sucks-chart}
#| fig-width: 10
#| fig-height: 8

teams_standings_suck %>%
  mutate(
    suck_category = case_when(
      suck_rank == 1 ~ "💩 Supreme Sucker",
      suck_rank <= 3 ~ "🤮 Major Suckage",
      suck_rank <= 6 ~ "😬 Moderate Suck",
      suck_rank <= 9 ~ "😐 Slight Suck",
      TRUE ~ "😎 Doesn't Suck"
    ),
    suck_category = factor(suck_category, levels = c(
      "😎 Doesn't Suck",
      "😐 Slight Suck", 
      "😬 Moderate Suck",
      "🤮 Major Suckage",
      "💩 Supreme Sucker"
    ))
  ) %>%
  ggplot(aes(x = reorder(team_name, -suck_index), y = suck_index, fill = suck_category)) +
  geom_col() +
  geom_text(aes(label = sprintf("%.2f", suck_index)), hjust = -0.2, size = 3.5) +
  coord_flip() +
  scale_fill_manual(values = c(
    "😎 Doesn't Suck"   = brand[["green"]],
    "😐 Slight Suck"    = brand[["slate"]],
    "😬 Moderate Suck"  = brand[["orange"]],
    "🤮 Major Suckage"  = "#E67E22",
    "💩 Supreme Sucker" = brand[["red"]]
  )) +
  labs(title = "🤡 Official \"Who Sucks?\" Power Rankings",
       subtitle = "Scientific measurement of fantasy football incompetence",
       x = NULL,
       y = "Suck Index (Higher = More Suck)") +
  theme(legend.position = "right") +
  ylim(min(teams_standings_suck$suck_index) - 0.5,
       max(teams_standings_suck$suck_index) * 1.15)
```

```{r suck-components-chart}
#| fig-width: 10
#| fig-height: 8

# Show breakdown of suck components
suck_components <- teams_standings_suck %>%
  select(team_name, suck_win_pct, suck_pf) %>%
  pivot_longer(cols = starts_with("suck_"), 
               names_to = "component", 
               values_to = "value") %>%
  mutate(component = case_when(
    component == "suck_win_pct" ~ "Poor Win %",
    component == "suck_pf" ~ "Low Scoring",
    TRUE ~ component
  ))

ggplot(suck_components, aes(x = reorder(team_name, value), y = value, fill = component)) +
  geom_col(position = "stack") +
  coord_flip() +
  scale_fill_manual(values = c("Poor Win %"  = brand[["red"]],
                               "Low Scoring" = brand[["orange"]])) +
  labs(title = "Suck Index Breakdown by Component",
       subtitle = "What makes each team suck?",
       x = NULL,
       y = "Cumulative Suck Score")
```

::: {.callout-note icon="false"}
## 📊 Methodology

The Suck Index is calculated by standardizing (z-scores) two metrics:

1.  **Win Percentage** (negated) - Losing teams get positive suck points
2.  **Points For** (negated) - Low-scoring teams get positive suck points

Both components are weighted equally and summed. This is completely arbitrary and designed to generate maximum trash talk. 🗑️
:::

# 📈 Key Insights

```{r insights, results='asis'}
# Generate insights

player_stats <- data$player_stats

# Calculate team scores (starters only)
starters <- player_stats %>% filter(lineup_group == "START")

bench_players <- player_stats %>%
  filter(lineup_group == "BENCH") %>%
  arrange(desc(points)) %>%
  head(10)

mvp <- starters %>% arrange(desc(points)) %>% head(1)
worst_starter <- starters %>% arrange(points) %>% head(1)
best_bench <- bench_players %>% head(1)
close_games <- matchups[abs(matchups$away_score - matchups$home_score) < 5, ]
blowouts <- matchups[abs(matchups$away_score - matchups$home_score) > 30, ]
```

::: {.callout-important icon="false"}
## Week `r WEEK` Highlights

- **Week MVP:** `r mvp$player_name` (`r mvp$position`, `r mvp$nfl_team`) scored `r sprintf("%.2f", mvp$points)` points for `r mvp$fantasy_team_name`

- **Biggest Disappointment:** `r worst_starter$player_name` (`r worst_starter$position`, `r worst_starter$nfl_team`) scored only `r sprintf("%.2f", worst_starter$points)` points for `r worst_starter$fantasy_team_name`

- **Biggest Missed Opportunity:** `r best_bench$player_name` (`r best_bench$position`, `r best_bench$nfl_team`) left `r sprintf("%.2f", best_bench$points)` points on the bench for `r best_bench$fantasy_team_name`

- **Score Range:** `r sprintf("%.2f", max(team_scores$total_points) - min(team_scores$total_points))` point difference between highest and lowest scoring teams

- **Close Games:** `r nrow(close_games)` matchup(s) decided by less than 5 points

- **Blowouts:** `r nrow(blowouts)` matchup(s) with 30+ point margins
:::

# 📝 Week `r WEEK` Storylines

 Storylines still to come -- too lazy

------------------------------------------------------------------------

*Data sourced from Fleaflicker API.*
